---
title: "use"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{use}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# `ormr`

`ormr` allows to work with Python installed to a custom location,
using only a single point of contact.

```{r setup}
library(ormr)
```

We use only one point of contact, `ormr_folder_name`,
which is the folder where `ormr` installs the Python environment and packages
needed:

```{r get_ormr_folder_name}
if (is_conda_installed()) {
  ormr_folder_name <- get_default_ormr_folder_name()
} else {
  ormr_folder_name <- "python3"
}
```

Note we use the default `ormr_folder_name`, as this package
needs to only use one Python version, in both this
vignette and its tests.

# Goal

The goal of this vignette is to show how to use `ormr` 
to run an example Python script, 
where Python is installed to a custom location.

Here is the example Python script we want to run:

```{r show_python_script}
python_script_path <- system.file("extdata", "scipy_example.py", package = "ormr")
readLines(python_script_path)
```

As a spoiler, it is demonstrated here that the script *maybe*
cannot be run yet:

```{r cannot_run_python_script_yet}
try(
  run_python_script(
    ormr_folder_name = ormr_folder_name,
    python_script_path = python_script_path
  ), 
  silent = FALSE
)
```

When using the default `ormr` Conda environment, `scipy`
may actually be installed.

# Overview

These are the steps to achieve the goal:

 1. Install Python packages
 2. Run a Python script
 
Note that there is no need to create a Conda environment:
this is what `ormr` does for you. `ormr` uses **eager loading**,
which is the opposite of `reticulate`'s lazy loading.

## 1. Install Python packages within that Conda environment

Currently, these packages are installed:

```{r}
installed_python_packages <- ormr::get_installed_python_packages(
  ormr_folder_name = ormr_folder_name
)
knitr::kable(installed_python_packages)
```

We are going to install `scipy`, which is a small package:

```{r}
package_name <- "scipy"
```

We can verify that it *may* not be installed yet:

```{r}
is_python_package_installed(
  ormr_folder_name = ormr_folder_name,
  package_name = package_name
)
```

The package *may* be installed when using the default
`ormr` Conda environment.

Also, running an Python script that requires `scipy` *may* fail now:

```{r}
try(
  run_python_script(
    ormr_folder_name = ormr_folder_name,
    python_script_path = python_script_path
  ),
  silent = FALSE
)
```

The script *may* pass when using the default
`ormr` Conda environment and the needed Python packages
are already installed.

Here, we install the package:

```{r}
ormr::install_python_packages(
  ormr_folder_name = ormr_folder_name,
  package_names = package_name
)
```

Now the Python package is installed:

```{r}
testthat::expect_true(
  ormr::is_python_package_installed(
    ormr_folder_name = ormr_folder_name,
    package_name = package_name
  )
)
```

## 2. Run a Python script with that Conda environment and packages

Great, with packages in place,
we run a Python script with those packages:

```{r}
testthat::expect_silent(
  ormr::run_python_script(
    ormr_folder_name = ormr_folder_name,
    python_script_path = python_script_path
  )
)
```

No error, so we can conclude it works!

# Cleaning up

The clean up, we throw away the `ormr` folder in which the magic happened.

```{r}
if (ormr_folder_name != get_default_ormr_folder_name()) {
  unlink(ormr_folder_name, recursive = TRUE)  
}
```
